babette: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-09 article.tex
spellcheck

\verb;babette; has 20 exported function to parse the BEAST2 output
files and analyse the created posterior. \verb;babette; gives the
same ESSes and summary statistics as Tracer. The data is formatted
as such, that it can easily be visualized using \verb;ggplot2; (for a trace,
similar to Tracer)
or \verb;phangorn; \cite{phangorn} (for the phylogenies in a posterior, simular to DensiTree).

@@

\verb;babette; allows for the same functionality of DensiTree.
DensiTree displays the phylogenies in a posterior at the same
time scale over one another, allowing to see the uncertainty in
topology and branch lengths. To vizualize the same in \verb;babette;:

@@

\verb;babette;'s development takes place on GitHub \cite{github},
\url{https://github.com/richelbilderbeek/babette}, 
which accomodates collaboration \cite{perez2016ten} 
and improves transparency \cite{gorgolewski2016practical}.
\verb;babette;'s GitHub facilitates feature requests and has a guidelines how to do so.

>>>>

\verb;babette; has 20 exported function to parse the BEAST2 output
files and analyse the created posterior. \verb;babette; gives the
same ESSes and summary statistics as Tracer. The data is formatted
as such, that it can easily be visualized using \verb;ggplot2; (for a trace,
similar to Tracer)
or \verb;phangorn; \cite{phangorn} (for the phylogenies in a posterior, similar to DensiTree).

@@

\verb;babette; allows for the same functionality of DensiTree.
DensiTree displays the phylogenies in a posterior at the same
time scale over one another, allowing to see the uncertainty in
topology and branch lengths. To visualize the same in \verb;babette;:

@@

\verb;babette;'s development takes place on GitHub \cite{github},
\url{https://github.com/richelbilderbeek/babette}, 
which accommodates collaboration \cite{perez2016ten} 
and improves transparency \cite{gorgolewski2016practical}.
\verb;babette;'s GitHub facilitates feature requests and has a guidelines how to do so.
